An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-06-20 Article/EconGrowth2.Rnw
Different size of trajectory graph.

<<LINEX_abg_traj_graph_IR, fig.pos="H", fig.align='center', fig.width=3, fig.height=2, fig.cap="LINEX trajectory for Iran.">>=
dataIR <- fortify(OrigModels$IR$linex$`iK+iL+iQ`)
triPlot(data=dataIR, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1990")
@

>>>>

<<LINEX_abg_traj_graph_IR, fig.pos="H", fig.align='center', fig.width=3, fig.height=1.5, fig.cap="LINEX trajectory for Iran.">>=
dataIR <- fortify(OrigModels$IR$linex$`iK+iL+iQ`)
triPlot(data=dataIR, grid_lines=5, x=alpha, y=beta, z=gamma, geom=geom_line, aes_string="colour = iYear + 1990")
@
